%-------------------------
% Resume in Latex
% Author : Nivesh Singh
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://niveshsingh.com/}{\Large Nivesh Singh}} & Email : \href{mailto:nivesh2@live.in}{nivesh2@live.in}\\
  \href{http://niveshsingh.com/}{http://niveshsingh.com} & Mobile : +91-880-069-1089 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Madan Mohan Malaviya University of Technology}{Gorakhpur, India}
      {B.Tech in Computer Science Engineering;  Grade:73\%}{Aug. 2010 - May. 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Self Employed}{Remote, IN}
      {Sr. Consultant}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem{TICK Stack, nashpay[SG]}
          {TICK Stack is an open source time series platform provides services and functionality to accumulate, analyze, and act on time series data; Developed in-house monitoring and alerting system for a crypto-currency payment gateway startup.}
        \resumeItem{Keycloak, nashpay[SG]}
          {Keycloak is a open source identity and access management system, alternative to AWS Cognito and IAM; Developed in-house IAM system for clients accessing the crypto-curreny payment gateway.}
        \resumeItem{AWS Serverless Stack, lovedWealth[US]}
          {An investment platform for parents built completely on top of AWS technologies. Managed and developed new modules using AWS stack. Technologies involved API Gateway, Cognito, Lambda, Step functions, AWS Batch, S3, Aurora, DynamoDB, SQS, SNS, SES, CloudWatch, GraphQL and node.js.}
        \resumeItem{MEAN Stack, goldcanvas[US]}
          {A premium marketplace for artist and collectors. Built the entire system and its design from scratch to production ready. Integrated with Stripe Connect and shippo for payments and shipping across US.}
        \resumeItem{SOAP+Node, dotd[AU]}
          {An equity management and investor communications firm. Worked on automating Australian company and business name registration process, integrating with ASIC(Australian Securities and Investments Commission) systems.}
      \resumeItemListEnd

    \resumeSubheading
      {Instarem}{Mumbai, IN}
      {Software Developer}{Dec 2016 - May 2018}
      \resumeItemListStart
        \resumeItem{KYC Engine}
          {Automate KYC for various corridors for fast customer on boarding, integrated with Jumio for Document/FaceMatch verification and Trulioo for Identity \& Address verification.}
        \resumeItem{Compliance Engine}
          {Built multi-level compliance check triggers integrated in database level, integrated with Worldcheck \& trulioo for global watchlist compliance checks.}
        \resumeItem{Fuzzy Search}
          {For fuzzy matching of customer filled details with OFAC sanctioned banks and blacklisted regulatory list under compliance check using elastic search.}
        \resumeItem{Transaction Processing}
          {Designed and Developed transaction flow and processing of payments for both B2C \& B2B systems.}
        \resumeItem{Payment Gateway}
          {Integrated with various banks and payment gateways across various countries. Integrated with REST API, SOAP-XML and SFTP based payment systems.}
        \resumeItem{Service Discovery}
          {Developed in-house service discovery bus using rabbitMQ to decouple various microservices.}
      \resumeItemListEnd

    \resumeSubheading
      {Tech Mahindra}{Delhi NCR, IN}
      {Software Engineer}{Sep 2014 - Nov 2016}
      \resumeItemListStart
        \resumeItem{AT\&T Project}
          {Rewrite of entire enterprise Java application, WAO(Web Access Ordering, wholesale web portal for AT\&T), built on IBM Websphere, to a new and robust version.}
        \resumeItem{Technologies Used}
          {J2EE, Struts 2, JMS, JAXM, EJB, Hibernate, JMeter, Jenkins, Oracle SQL, PL/SQL and BO \& DAO design pattern.}
          
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Mulit-ICO Decentralized app}
      {Smart contract for a multi-ICO creation portal built in EYHackathon 2017.}
%    \resumeSubItem{Market Maker}
%      {A Bitcoin wallet for customers, integrated with BitGo multi-signature wallet and GDAX trade api.}
    \resumeSubItem{IOT Switch}
      {Control home devices using WEB REST API, built using AWS IOT, NODE.JS and mediaTek device.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C, C++, Java, Javascript}
      \hfill
      \textbf{Technologies}{: MEAN, J2EE, ELK, TICK, AWS, Azure}
    }
  \resumeSubHeadingListEnd
  
%--------CURRENT INTEREST------------
\section{Current Interest}
  \resumeSubHeadingListStart
    \item{
      \textbf{Domain}{: Blockchain and FinTech}
      \hfill
      \textbf{Programming language}{: GO and Elxir}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
